Concentration of Maxima and Fundamental Limits in High-Dimensional Testing and Inference

### 2021-04-19 5.Bayes.optimality/5.Bayes_optimality_and_minimax.tex
"approve" changes on generalized support set size

For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that \stilian{$|S_p| = \lfloor \ell(p) p^{1-\beta} \rfloor$}{$|S_p| = \lfloor p^{1-\beta}\rfloor$}, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ (recall \eqref{eq:minimax-signal-config-under}),
where $r<\overline{r}<f_{\mathrm{E}}(\beta)$, and according to Theorem \ref{thm:necessary}, we obtain 
$\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
\end{proof}

@@

For any distribution $\pi$ (with a slight abuse of notation) over the parameter space $\Theta_p^+\times D(F)$, we have
\begin{equation} \label{eq:minimax-over-dependence-under-proof}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) 
\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_{\pi} \P(\widehat{S}_p \neq S_p),
\end{equation}
since the supremum is bounded from below by expectations.
In particular, define $\pi$ to be the uniform distribution over the configurations $\Theta_p^*\times I(f)$, where
\begin{align*}
    \Theta_p^* &=
    \{\mu\in\mathbb{R}^d:\;|S_p|=\stilian{\lfloor \ell(p)p^{1-\beta} \rfloor}{\lfloor p^{1-\beta}\rfloor},\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<f_{\mathrm{E}}(\beta)\},
\end{align*}
and 
% \begin{align*}
%     I(f)&=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{are independently and identically distributed}\\
%     &\quad\quad\text{with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
% \end{align*}
\begin{equation*}
    I(f)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{\ac{iid} with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
\end{equation*}

>>>>

For the second statement \eqref{eq:point-wise-minimax-below}, since $\underline{r}<f_{\mathrm{E}}(\beta)$, we can pick a sequence $\mu^*\in\Theta_p^+(\beta, \underline{r})$ such that $|S_p| = \lfloor \ell(p) p^{1-\beta} \rfloor$, with signals having the same signal size $\mu(i)=(2r\log{p})^{1/\nu}$ for all $i\in S_p$, where $\underline{r}<{r}<f_{\mathrm{E}}(\beta)$.
For this particular choice of $\mu^*$ we have $\mu^*\in\Theta_p^-(\beta, \overline{r})$ (recall \eqref{eq:minimax-signal-config-under}),
where $r<\overline{r}<f_{\mathrm{E}}(\beta)$, and according to Theorem \ref{thm:necessary}, we obtain 
$\lim_{p\to\infty} \inf_{\widehat{S}_p\in \cal T} \mathbb P[\widehat{S}_p \neq S_p] = 1$, for all dependence structures in the URS class.
\end{proof}

@@

For any distribution $\pi$ (with a slight abuse of notation) over the parameter space $\Theta_p^+\times D(F)$, we have
\begin{equation} \label{eq:minimax-over-dependence-under-proof}
    \liminf_{p\to\infty} \inf_{\widehat{S}_p} \sup_{\substack{\mu\in\Theta_p^+(\beta, \underline{r})\\ {\cal E}\in D(F)}} \P(\widehat{S}_p \neq S_p) 
\ge \liminf_{p\to\infty} \inf_{\widehat{S}_p} \E_{\pi} \P(\widehat{S}_p \neq S_p),
\end{equation}
since the supremum is bounded from below by expectations.
In particular, define $\pi$ to be the uniform distribution over the configurations $\Theta_p^*\times I(f)$, where
\begin{align*}
    \Theta_p^* &=
    \{\mu\in\mathbb{R}^d:\;|S_p|=\lfloor \ell(p)p^{1-\beta} \rfloor,\;\mu(i)=0\;\text{for all }i\not\in S, \;\text{and}\\
    &\quad\quad\mu(i) = (\nu{r}\log{p})^{1/\nu}\;\text{for all }i\in S,\;\text{where}\;\underline{r}<r<f_{\mathrm{E}}(\beta)\},
\end{align*}
and 
% \begin{align*}
%     I(f)&=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{are independently and identically distributed}\\
%     &\quad\quad\text{with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
% \end{align*}
\begin{equation*}
    I(f)=\{{\cal E}=(\epsilon_p(i))_p:\;\epsilon_p(i)\;\text{\ac{iid} with density}\; f(x)\propto \exp\{-|x|^\nu/\nu\}\}.
\end{equation*}
